Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - half of ch5 result

\usepackage{xcolor}
\usepackage{colortbl,booktabs}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{wrapfig} % text around figures
\usepackage{amssymb} % \mathbbstarcra
\usepackage[final]{listings} % algorithms formated in code
\usepackage{enumitem} % compact imte lists
\usepackage{subcaption} % for subfigure (figures side-by-side)
\usepackage{mathtools}
\usepackage{soul}
\usepackage[detect-all]{siunitx} % Aligning numbers by decimal points in table columns
\usepackage{bm}

@@

% ####################################################################################################################################
\chapter{Experiment Result}
% ####################################################################################################################################

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_10_result.png}
    \caption{Accuracy}
    \label{fig:Accuracy}
\end{figure}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
                       &      & \multicolumn{5}{l|}{The number of neurans} \\ \hline
Test                   & n    & 16    & 32    & 64      & 128      & 256   \\ \hline
\multirow{4}{*}{1}     & 1    & 0.5   & 0.25  & 1.0     & 0.5      & 0.5   \\ \cline{2-7}
                       & 2    & 0.75  & 0.75  & 0.5     & 0.5      & 0.5   \\ \cline{2-7}
                       & 3    & 1.0   & 0.5   & 0.5     & 0.75     & 0.5   \\ \cline{2-7}
                       & 4    & 0.5   & 0.5   & 0.75    & 0.5      & 0.5   \\ \hline
\multirow{4}{*}{2}     & 1    & 0.5   & 0.75  & 0.75    & 0.75     & 0.75  \\ \cline{2-7}
                       & 2    & 0.25  & 0.25  & 0.75    & 0.5      & 0.25  \\ \cline{2-7}
                       & 3    & 0.5   & 0.5   & 0.25    & 0.75     & 0.25  \\ \cline{2-7}
                       & 4    & 0.25  & 0.25  & 0.5     & 0.25     & 0.75  \\ \hline
\multirow{4}{*}{3}     & 1    & 0.75  & 0.25  & 1.0     & 0.75     & 0.25  \\ \cline{2-7}
                       & 2    & 0.25  & 0.5   & 0.75    & 0.5      & 1.0   \\ \cline{2-7}
                       & 3    & 0.5   & 0.75  & 0.75    & 0.5      & 0.5   \\ \cline{2-7}
                       & 4    & 0.5   & 0.25  & 0.75    & 0.75     & 0.5   \\ \hline
\multirow{4}{*}{4}     & 1    & 0.75  & 0.5   & 0.5     & 0.5      & 0.5   \\ \cline{2-7}
                       & 2    & 0.25  & 0.5   & 0.5     & 1.0      & 0.25  \\ \cline{2-7}
                       & 3    & 0.0   & 0.75  & 1.0     & 0.75     & 0.25  \\ \cline{2-7}
                       & 4    & 0.75  & 0.75  & 0.75    & 0.25     & 0.75  \\ \hline
\multicolumn{2}{|l|}{Average} & 0.5   & 0.5   & 0.6875  & 0.59375  & 0.5   \\ \hline
\end{tabular}
\caption{Raw 1/10 Result Summary}
\label{Raw 1/10 Result Summary}
\end{table}

>>>>

\usepackage{xcolor}
\usepackage{colortbl,booktabs}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{wrapfig} % text around figures
\usepackage{amssymb} % \mathbbstarcra
\usepackage[final]{listings} % algorithms formated in code
\usepackage{enumitem} % compact imte lists
\usepackage{subcaption} % for subfigure (figures side-by-side)
\usepackage{mathtools}
\usepackage{soul}
\usepackage[detect-all]{siunitx} % Aligning numbers by decimal points in table columns
\usepackage{bm}
\usepackage{multirow}

@@

% ####################################################################################################################################
\chapter{Experiment Result}
% ####################################################################################################################################
This chapter summarizes results from all experiments. Experiments are divided to two parts: 1) experiments with {\em filtered dataset} 2) experiments with {\em raw dataset}. First part of experiments used {\em first model} which only has LSTM. Each experiments used 5 different number of neurons: 16, 32, 64, 128, and 256. Second part of experiments used {\em second model} which has SAE and {\em third model} which has MAE then compared result of three models.

\section{Experiments with {\em filtered dataset}}
The first part of experiments used {\em filtered dataset} which has chosen 23 features. The dataset was re-sampled by 1 over 10, 1 over 20, and 1 over 50 with three different methods: {\em last}, {\em mean}, and {\em gaussian} so it was 9 different re-sampled datasets.

\subsection{Resample 1 over 50}
This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 50. Figure \ref{fig:filter_1_50} shows average accuracy of four tests on different number of neurons in LSTM hidden layer. Table \ref{tbl:last_1_50}, Table \ref{tbl:mean_1_50}, and Table \ref{tbl:gaussian_1_50} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively. Table \ref{tbl:last_1_50_time}, Table \ref{tbl:mean_1_50_time}, and Table \ref{tbl:gaussian_1_50_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.

The best performance was from {\em last} method with 16 number of neurons. The accuracy of this was 0.59375 (59.375\%). The worst performance was from {\em gaussian} method with 64 number of neurons. It was 0.40625 (40.625\%). Many accuracy were below 0.5 (50\%) and total average accuracy is 0.492708 (49.2708\%). The experiments with 1 over 50 re-sampled data took short time than experiments with 1 over 20 and 1 over 10 re-sampled data on later of this chapter.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_50_result.png}
    \caption{Result of 1 over 50 from {\em filtered dataset}}
    \label{fig:filter_1_50}
\end{figure}

\begin{table}[!t]
\centering
\caption{{\em last} method on 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:last_1_50}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                              \\ \cline{3-7} 
                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 1            & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7} 
                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25        & 0.75         \\ \cline{2-7} 
                      & 3                   & 0.75         & 0.25         & 0.25         & 0.75        & 0.75         \\ \cline{2-7} 
                      & 4                   & 0.75         & 0.75         & 0.5          & 0.75        & 0.75         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5          & 0            & 0.75         & 0.75        & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.25         & 0.25         & 0.5          & 0.5         & 0.25         \\ \cline{2-7} 
                      & 3                   & 0.75         & 0.25         & 0.25         & 0.5         & 1            \\ \cline{2-7} 
                      & 4                   & 0.5          & 0.5          & 0.75         & 0.5         & 0.5          \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5          & 0.75         & 0.5          & 0.75        & 0            \\ \cline{2-7} 
                      & 2                   & 0.5          & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.5          & 0.5          & 0.25         & 0.25        & 0.5          \\ \cline{2-7} 
                      & 4                   & 0.75         & 0.75         & 0.75         & 0.25        & 0.5          \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.75         \\ \cline{2-7} 
                      & 3                   & 0.5          & 0.75         & 0.75         & 0.75        & 0.25         \\ \cline{2-7} 
                      & 4                   & 1            & 0.75         & 0.5          & 0.5         & 0.5          \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.484375     & 0.546875     & 0.5625      & 0.515625     \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em mean} method on 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:mean_1_50}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                             \\ \cline{3-7} 
                      &                     & 16          & 32           & 64          & 128          & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5          & 0           & 0.25         & 0.25         \\ \cline{2-7} 
                      & 2                   & 0.5         & 0.5          & 0.25        & 0.5          & 0.5          \\ \cline{2-7} 
                      & 3                   & 0           & 0.75         & 0.5         & 0.25         & 0.75         \\ \cline{2-7} 
                      & 4                   & 0           & 0.5          & 0.25        & 0.25         & 0.25         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5          & 0.5         & 0.5          & 0            \\ \cline{2-7} 
                      & 2                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.75         \\ \cline{2-7} 
                      & 3                   & 0.5         & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.25         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.25         & 0.5         & 0.5          & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.25        & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7} 
                      & 3                   & 0.5         & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7} 
                      & 4                   & 0.75        & 0.5          & 0.5         & 0.75         & 0.5          \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5          & 0.75        & 0.25         & 1            \\ \cline{2-7} 
                      & 2                   & 0.75        & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.5         & 0.25         & 0.25        & 0.25         & 0.75         \\ \cline{2-7} 
                      & 4                   & 0.5         & 0.75         & 0.75        & 0.25         & 0.75         \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.421875    & 0.5          & 0.484375    & 0.421875     & 0.484375     \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.218303115 & 0.1825741858 & 0.213478141 & 0.1983000672 & 0.2656556355 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em gaussian} method on 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:gaussian_1_50}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                              \\ \cline{3-7} 
                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.25         \\ \cline{2-7} 
                      & 2                   & 0.75         & 0.75         & 0.25         & 0.75        & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.25         & 1            & 0.25         & 0.5         & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.75         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.75         & 0.25         & 0.5          & 0.5         & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.5          & 0.75         & 0.25         & 0.5         & 0.25         \\ \cline{2-7} 
                      & 3                   & 0.5          & 0.5          & 0.5          & 0           & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.75         & 0            & 0.75         & 0.75        & 1            \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5         & 0.25         \\ \cline{2-7} 
                      & 2                   & 0.75         & 0.25         & 0.5          & 0           & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.75         \\ \cline{2-7} 
                      & 4                   & 0.5          & 0.25         & 0.25         & 0.75        & 0.75         \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7} 
                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5         & 0.25         \\ \cline{2-7} 
                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.5          \\ \cline{2-7} 
                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.25         \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.578125     & 0.421875     & 0.40625      & 0.515625    & 0.453125     \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em last} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:last_1_50_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:18:41                      & 0:20:07                      & 0:23:00                      & 0:39:32                      & 0:54:27                      \\ \hline
2                          & 0:16:28                      & 0:18:18                      & 0:22:19                      & 0:34:39                      & 0:47:47                      \\ \hline
3                          & 0:16:25                      & 0:18:17                      & 0:22:15                      & 0:34:38                      & 0:49:43                      \\ \hline
4                          & 0:16:36                      & 0:18:28                      & 0:23:19                      & 0:34:01                      & 0:53:42                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em mean} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:mean_1_50_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:18:33                      & 0:19:09                      & 0:23:59                      & 0:34:57                      & 0:51:25                      \\ \hline
2                          & 0:16:25                      & 0:17:16                      & 0:22:33                      & 0:35:32                      & 0:47:26                      \\ \hline
3                          & 0:16:48                      & 0:18:07                      & 0:22:46                      & 0:34:57                      & 0:52:14                      \\ \hline
4                          & 0:16:39                      & 0:18:36                      & 0:23:23                      & 0:36:05                      & 0:51:44                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em gaussian} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:gaussian_1_50_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:18:05                      & 0:18:33                      & 0:22:40                      & 0:37:31                      & 0:54:11                      \\ \hline
2                          & 0:16:24                      & 0:18:08                      & 0:22:19                      & 0:35:22                      & 0:48:40                      \\ \hline
3                          & 0:16:17                      & 0:18:00                      & 0:22:18                      & 0:35:12                      & 0:53:03                      \\ \hline
4                          & 0:16:28                      & 0:18:39                      & 0:22:33                      & 0:34:25                      & 0:54:57                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:16:49} & \multicolumn{1}{l|}{0:18:20} & \multicolumn{1}{l|}{0:22:28} & \multicolumn{1}{l|}{0:35:38} & \multicolumn{1}{l|}{0:52:43} \\ \hline
\end{tabular}
\end{table}

\subsection{Resample 1 over 20}
This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 20. Figure \ref{fig:filter_1_20} shows average accuracy of four tests on different number of neurons in LSTM hidden layer. Table \ref{tbl:last_1_20}, Table \ref{tbl:mean_1_20}, and Table \ref{tbl:gaussian_1_20} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively. Table \ref{tbl:last_1_20_time}, Table \ref{tbl:mean_1_20_time}, and Table \ref{tbl:gaussian_1_20_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.

The best performance was from {\em mean} method with 32 and 256 number of neurons. The accuracy of this was 0.59375 (59.375\%) as same as best performance from experiments with 1 over 50 re-sampled data. The worst performance was also from {\em mean} method with 128 number of neurons. It was 0.375 (37.5\%) and worse than the worst performance from experiments with 1 over 50 re-sampled data. However, the total average was 0.515625 (51.5625\%) which was slightly higher than the total average 0.492708 (49.2708\%) from experiments with 1 over 50 re-sampled data because size of 1 over 20 re-sampled data is 2.5 times more than size of 1 over 50 re-sampled data. More amount data also affected to test time. Even size of the data is 2.5 times more, test time took more than 2.5 times than test time from experiments with 1 over 50 re-sampled data.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_20_result.png}
    \caption{Result of 1 over 20 from {\em filtered dataset}}
    \label{fig:filter_1_20}
\end{figure}

\begin{table}[!t]
\centering
\caption{{\em last} method on 1 over 20 Re-sampled {\em filtered dataset}}
\label{tbl:last_1_20}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                             \\ \cline{3-7} 
                      &                     & 16           & 32           & 64          & 128         & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.75         & 0.5          & 0.25        & 0.5         & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.5          & 0.25         & 0.75        & 0.5         & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.5          & 0.25         & 0.75        & 0.25        & 0.5          \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.25         & 1            & 0.25        & 0.5         & 0            \\ \cline{2-7} 
                      & 2                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.75         \\ \cline{2-7} 
                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.5          \\ \cline{2-7} 
                      & 4                   & 0.5          & 0.5          & 0.25        & 0.25        & 0.25         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.25         & 0.75         & 0.5         & 0.5         & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.25         & 0            & 0.75        & 0.5         & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.5          & 0.5          & 0.5         & 0.75        & 0.75         \\ \cline{2-7} 
                      & 4                   & 0.25         & 0.5          & 0.5         & 0.25        & 0.75         \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5         & 0.25        & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.25         & 0.75         & 1           & 0.75        & 0.25         \\ \cline{2-7} 
                      & 3                   & 0.75         & 0.75         & 0.25        & 0.75        & 1            \\ \cline{2-7} 
                      & 4                   & 0.75         & 0.25         & 0.5         & 1           & 0.5          \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.484375     & 0.453125     & 0.515625    & 0.515625    & 0.5          \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.1929756029 & 0.2617051458 & 0.213478141 & 0.213478141 & 0.2415229458 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em mean} method on 1 over 20 Re-sampled {\em filtered dataset}}
\label{tbl:mean_1_20}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                           \\ \cline{3-7} 
                      &                     & 16       & 32           & 64           & 128          & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5      & 0.5          & 0.5          & 0.25         & 0.75         \\ \cline{2-7} 
                      & 2                   & 0.25     & 0.5          & 0.25         & 0            & 1            \\ \cline{2-7} 
                      & 3                   & 0.75     & 0.25         & 0.75         & 0.25         & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.75     & 1            & 0.25         & 0.75         & 0.75         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.75     & 0.75         & 0.5          & 0.5          & 0.75         \\ \cline{2-7} 
                      & 2                   & 0.75     & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.5      & 0.75         & 0.75         & 0.5          & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.5      & 0.5          & 0.75         & 0.5          & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5      & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.75     & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.25     & 0.25         & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
                      & 4                   & 0.5      & 0.5          & 0.5          & 0.75         & 0.75         \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5      & 0.5          & 0.75         & 0.25         & 1            \\ \cline{2-7} 
                      & 2                   & 0.25     & 1            & 0.5          & 0.75         & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.5      & 0.5          & 0.5          & 0            & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.75     & 0.5          & 0.5          & 0.25         & 0.5          \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.546875 & 0.59375      & 0.53125      & 0.375        & 0.59375      \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.1875   & 0.2561737691 & 0.1547847968 & 0.2581988897 & 0.2393567769 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em gaussian} method on 1 over 20 Re-sampled {\em filtered dataset}}
\label{tbl:gaussian_1_20}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                               \\ \cline{3-7} 
                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.25         & 0.25         & 0.25         & 0.5          & 0.75         \\ \cline{2-7} 
                      & 3                   & 0.75         & 1            & 0.75         & 0.25         & 0            \\ \cline{2-7} 
                      & 4                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.25         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.25         & 1            \\ \cline{2-7} 
                      & 2                   & 1            & 0.75         & 0.75         & 0.75         & 0.25         \\ \cline{2-7} 
                      & 3                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.75         & 0.25         & 1            & 0.5          & 0.25         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7} 
                      & 2                   & 0            & 0.5          & 0.25         & 0.25         & 0.5          \\ \cline{2-7} 
                      & 3                   & 0.75         & 0            & 0.5          & 0.75         & 0.25         \\ \cline{2-7} 
                      & 4                   & 0.5          & 1            & 0.5          & 0.25         & 0.75         \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 1            & 0.75         & 0.5          \\ \cline{2-7} 
                      & 2                   & 0.5          & 0.75         & 0.25         & 0.25         & 0.25         \\ \cline{2-7} 
                      & 3                   & 0.5          & 0            & 0.5          & 0.5          & 0.75         \\ \cline{2-7} 
                      & 4                   & 0.5          & 0.25         & 0.75         & 0.5          & 0.5          \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.53125      & 0.578125     & 0.46875      & 0.453125     \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.2393567769 & 0.3145764348 & 0.2536196299 & 0.2015564437 & 0.2617051458 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em last} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
\label{tbl:last_1_20_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:45:44                      & 1:00:53                      & 1:31:39                      & 2:12:21                      & 3:44:16                      \\ \hline
2                          & 1:02:02                      & 1:03:06                      & 1:34:55                      & 2:13:50                      & 3:46:06                      \\ \hline
3                          & 0:44:21                      & 0:54:35                      & 1:29:29                      & 2:19:05                      & 3:51:18                      \\ \hline
4                          & 1:01:21                      & 0:56:54                      & 1:27:21                      & 2:16:57                      & 3:54:49                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:53:22} & \multicolumn{1}{l|}{0:58:52} & \multicolumn{1}{l|}{1:30:51} & \multicolumn{1}{l|}{2:15:33} & \multicolumn{1}{l|}{3:49:07} \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em mean} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
\label{tbl:mean_1_20_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:47:23                      & 0:59:46                      & 1:22:46                      & 2:10:24                      & 3:41:00                      \\ \hline
2                          & 0:45:34                      & 1:01:17                      & 1:33:30                      & 2:21:38                      & 3:52:10                      \\ \hline
3                          & 0:46:22                      & 0:53:08                      & 1:24:04                      & 2:11:51                      & 3:44:19                      \\ \hline
4                          & 0:54:35                      & 1:04:00                      & 1:27:45                      & 2:12:49                      & 3:49:12                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:48:29} & \multicolumn{1}{l|}{0:59:33} & \multicolumn{1}{l|}{1:27:01} & \multicolumn{1}{l|}{2:14:11} & \multicolumn{1}{l|}{3:46:40} \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em gaussian} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
\label{tbl:gaussian_1_20_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:47:04                      & 0:57:12                      & 1:24:38                      & 2:09:36                      & 3:46:59                      \\ \hline
2                          & 0:56:09                      & 0:55:51                      & 1:32:44                      & 2:19:37                      & 4:00:33                      \\ \hline
3                          & 0:46:57                      & 0:56:07                      & 1:29:21                      & 2:15:57                      & 3:47:52                      \\ \hline
4                          & 0:45:48                      & 1:00:38                      & 1:27:35                      & 2:28:19                      & 3:35:48                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:49:00} & \multicolumn{1}{l|}{0:57:27} & \multicolumn{1}{l|}{1:28:35} & \multicolumn{1}{l|}{2:18:22} & \multicolumn{1}{l|}{3:47:48} \\ \hline
\end{tabular}
\end{table}

\subsection{Resample 1 over 10}
This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 10. Figure \ref{fig:filter_1_10} shows average accuracy of four tests on different number of neurons in LSTM hidden layer. Table \ref{tbl:last_1_10}, Table \ref{tbl:mean_1_10}, and Table \ref{tbl:gaussian_1_10} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively. Table \ref{tbl:last_1_10_time}, Table \ref{tbl:mean_1_10_time}, and Table \ref{tbl:gaussian_1_10_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.

The best performance was from {\em last} method with 64 number of neurons. The accuracy of this was 0.6875 (68.75\%) and it was also the best accuracy from all experiments. The worst performance was also from {\em gaussian} method with 32 number of neurons. It was 0.40625 (40.625\%). The total average was 0.540625 (54.0625\%). Therefore, overall performance from experiments with 1 over 10 gave better result than from experiments with 1 over 20 and 1 over 50 re-sampled data. This is because 1 over 10 re-sampled data had largest amount of data and it caused better performance. However, test time increased as size of data increased. Especially, experiments with 256 neurons in LSTM hidden layer took average 6 hours 48 miniatures and total time from 12 experiments with 256 neurons took more than 3 days.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_10_result.png}
    \caption{Result of 1 over 10 from {\em filtered dataset}}
    \label{fig:filter_1_10}
\end{figure}
